---
output: github_document
---
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/thankr)](https://cran.r-project.org/package=thankr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/dirkschumacher/thankr?branch=master&svg=true)](https://ci.appveyor.com/project/dirkschumacher/thankr)
[![Travis-CI Build Status](https://travis-ci.org/dirkschumacher/thankr.svg?branch=master)](https://travis-ci.org/dirkschumacher/thankr)
[![Coverage Status](https://img.shields.io/codecov/c/github/dirkschumacher/thankr/master.svg)](https://codecov.io/github/dirkschumacher/thankr?branch=master)
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(repos = "https://cran.r-project.org")
```
# thankr

> standing on the shoulders of giants

Find out what packages you use and maybe thank the authors :)


## Install

### From CRAN
```{r, eval=FALSE}
install.packages("thankr")
```

### Latest development version
```{r, eval=FALSE}
devtools::install_github("dirkschumacher/thankr")
```

## Usage

```{r}
library(thankr)
```


```{r, eval=FALSE}
# identifies the packages currently loaded in your session
shoulders() # equal to shoulders("session")
```


```{r, eval=FALSE}
# shows all maintainers of your package library
shoulders("library")
```

```{r, eval=FALSE}
# find out about a specific package
# by default it lists all dependencies of that package as well
shoulders("package", "ropenaq", include_dependencies = FALSE)
shoulders("package", "ropenaq")
```

## Only in the development version

Everything here is still work in progress. Any feedback appreciated.

Find out what packages you have already starred on Github. Inspired by the node module [appreciate](https://github.com/musically-ut/appreciate).

```{r}
gh_starred(c("ropenaq", "Rcpp", "dplyr"))
```

If you are developing a package, you can call `appreciate` in your working directory. If there is a `DESCRIPTION` file, it parses it and checks if you have already starred the dependencies on github. The function fails, if the working directory does not contain a `DESCRIPTION` file.

```{r}
thankr::appreciate()
```


## Contributing

If you found a bug or want to propose a feature, feel free to visit the [issues page](https://github.com/dirkschumacher/thankr/issues).
